Cognate Priming: Report

### 2021-10-21 Rmd/report_00_participants_relaxed.Rmd

```{r participants_summary_relaxed_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp, test_language) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		test_language = md("**Language**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) 
	as_raw_html()
```

@@

```{r participants_cohort_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
# plot participants
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>%
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		),
		age_group = str_remove(age_group, " months")
	) %>%
	drop_na(valid_status) %>% 
	ggplot(aes(age_group, participant, colour = valid_status)) +
	facet_grid(location~lp, scales = "free") +
	geom_line(aes(group = interaction(lp, participant))) +
	geom_point(size = 2) +
	geom_hline(yintercept = 0.2, linetype = "dashed") +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
	theme(
		legend.position = "right",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	)
```

>>>>

```{r participants_summary_relaxed_tab_language, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp, test_language) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		test_language = md("**Language**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) %>% 
	as_raw_html()
```

@@

```{r participants_cohort_relaxed, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=6, out.width="100%"}
# plot participants
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>%
	mutate(
		valid_status = case_when(
			valid_participant & !is.na(vocab_size_l1) ~ "Valid (+ CDI)",
			valid_participant & is.na(vocab_size_l1) ~ "Valid (no CDI)",
			!valid_participant ~ "Not valid"
		),
		age_group = str_remove(age_group, " months")
	) %>%
	drop_na(valid_status) %>% 
	ggplot(aes(age_group, participant, colour = valid_status)) +
	facet_grid(location~lp, scales = "free") +
	geom_line(aes(group = interaction(lp, participant))) +
	geom_point(size = 2) +
	geom_hline(yintercept = 0.2, linetype = "dashed", colour = "white") +
	labs(x = "Age (months)", y = "Exposure to 2nd language", fill = "Validity status") +
	theme(
		legend.position = "right",
		legend.title = element_blank(),
		axis.text = element_text(size = 10),
		axis.title.y = element_blank(),
		axis.text.y = element_blank(),
		axis.ticks.y = element_blank()
	)
```

### 2021-10-21 Rmd/report_00_participants_stringent.Rmd

>>>>

```{r participants_summary_stringent_tab, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
participants_relaxed %>% 
	left_join(distinct(attrition_relaxed, participant, valid_participant)) %>% 
	filter(valid_participant) %>% 
	drop_na(valid_participant) %>% 
	count(location, age_group, lp) %>% 
	pivot_wider(names_from = "age_group", values_from = c("n"), values_fill = 0) %>% 
	gt(groupname_col = "location") %>% 
	cols_label(
		lp = md("**Language profile**"),
		`21 months` = md("**21 months**"),
		`25 months` = md("**25 months**"),
		`30 months` = md("**30 months**")
	) %>% 
	as_raw_html()

```

### 2021-10-21 Rmd/report_04_gca_relaxed.Rmd

vcov(fit) %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
	geom_tile() +
	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
	scale_fill_distiller(limits = c(-1, 1)) +
	coord_equal() +
	theme(
		legend.position = "top",
		legend.text = element_text(size = 8),
		axis.title = element_blank(),
		axis.text.y = element_text(hjust = 1, size = 7),
		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
	)

>>>>

vcov(fit) %>% 
	cov2cor() %>% 
	as.data.frame() %>% 
	rownames_to_column("term1") %>% 
	pivot_longer(-term1, names_to = "term2", values_to = ".value") %>% 
	filter(!grepl("time_bin", term1), !grepl("time_bin", term2)) %>% 
	ggplot(aes(fct_rev(term1), term2, fill = .value)) +
	geom_tile() +
	labs(x = "Term 1", y = "Term 2", fill = "Posterior correlation") +
	scale_fill_distiller(limits = c(-1, 1)) +
	coord_equal() +
	theme(
		legend.position = "top",
		legend.text = element_text(size = 8),
		axis.title = element_blank(),
		axis.text.y = element_text(hjust = 1, size = 7),
		axis.text.x = element_text(angle = 90, hjust = 1, size = 7)
	)

### 2021-10-21 Rmd/report_05_attrition_stringent.Rmd

### Attrition {.tabset }

@@

left_join(attrition, select(participants_stringent, age_group, location, lp, participant, date_test)) %>% 
	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(
		names_from = trial_type,
		values_from = valid_trial_count
	) %>% 
	clean_names() %>% 
	group_by(lp, location, age_group) %>% 
	summarise(
		cognate = mean(cognate, na.rm = TRUE),
		non_cognate = mean(non_cognate, na.rm = TRUE),
		unrelated = mean(unrelated, na.rm = TRUE),
		sum_n = sum(valid_participant, na.rm = TRUE),
		prop_n = mean(valid_participant, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	arrange(age_group, lp, location) %>% 
	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
	gt() %>% 
	tab_spanner(
		"Mean valid trials",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	tab_spanner(
		"N participants",
		c("sum_n", "n", "prop_n")
	) %>% 
	cols_label(
		age_group = "Age",
		lp = "Group",
		sum_n = "Valid",
		location = "Laboratory",
		n = "Tested",
		prop_n = "Valid (%)",
		cognate = "Cognate (8)",
		non_cognate = "Non-cognate (8)",
		unrelated = "Unrelated (16)"
	) %>% 
	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
	fmt_percent(c("prop_n")) %>% 
	fmt_number(c("n", "sum_n"), decimals = 0)

@@

```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
	group_by(location, participant, lp, age_group, valid_participant) %>% 
	summarise(
		valid = mean(valid_trial),
		invalid_gaze = mean(!valid_gaze),
		invalid_vocab = mean(!valid_vocab),
		.groups = "drop"
	) %>% 
	relocate(participant) %>% 
	gt() %>% 
	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		lp = "Lang. Profile",
		age_group = "Age",
		valid_participant = "Valid participant",
		valid = "Valid trials (%)",
		invalid_gaze = "Gaze (%)",
		invalid_vocab = "Vocabulary (%)"
	) %>% 
	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
	div(style='height:600px; overflow-y: scroll', .)
```

@@

```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
	count() %>% 
	ungroup() %>%
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
	clean_names() %>% 
	gt(groupname_col = c("location", "lp")) %>% 
	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
	cols_label(
		location = "Location",
		lp = "Group",
		trial_type = "Trial type",
		x21_months_not_valid = "Not valid",
		x21_months_valid = "Valid",
		x25_months_not_valid = "Not valid",
		x25_months_valid = "Valid",
		x30_months_not_valid = "Not valid",
		x30_months_valid = "Valid"
	)

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	ggplot(aes(trial_type, frequency_prime_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n),
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(size = 10),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_prime_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n),
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(size = 10),
		axis.title = element_blank()
	)
```

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	ggplot(aes(trial_type, familiarity_prime, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n),
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n),
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

### Raw data

```{r, echo = FALSE}
shinyAppFile(
	here("R", "gaze_app", "app.R"), 
	options = list(width = "100%", height = 700)
)
```

>>>>

@@

left_join(attrition, select(participants_stringent, age_group, location, lp, participant, date_test)) %>% 
	group_by(participant, lp, location, trial_type, date_test, age_group, valid_participant) %>% 
	summarise(valid_trial_count = sum(valid_trial, na.rm = TRUE),
			  .groups = "drop") %>% 
	pivot_wider(
		names_from = trial_type,
		values_from = valid_trial_count
	) %>% 
	clean_names() %>% 
	group_by(lp, location, age_group) %>% 
	summarise(
		cognate = mean(cognate, na.rm = TRUE),
		non_cognate = mean(non_cognate, na.rm = TRUE),
		unrelated = mean(unrelated, na.rm = TRUE),
		sum_n = sum(valid_participant, na.rm = TRUE),
		prop_n = mean(valid_participant, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	arrange(age_group, lp, location) %>% 
	relocate(age_group, lp, location, cognate, non_cognate, unrelated, sum_n, n, prop_n) %>% 
	gt() %>% 
	tab_spanner(
		"Mean valid trials",
		c("cognate", "non_cognate", "unrelated")
	) %>% 
	tab_spanner(
		"N participants",
		c("sum_n", "n", "prop_n")
	) %>% 
	cols_label(
		age_group = "Age",
		lp = "Group",
		sum_n = "Valid",
		location = "Laboratory",
		n = "Tested",
		prop_n = "Valid (%)",
		cognate = "Cognate (8)",
		non_cognate = "Non-cognate (8)",
		unrelated = "Unrelated (16)"
	) %>% 
	fmt_number(c("cognate", "non_cognate", "unrelated")) %>%
	fmt_percent(c("prop_n")) %>% 
	fmt_number(c("n", "sum_n"), decimals = 0) %>% 
	as_raw_html()

@@

```{r participants_attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	mutate(participant = str_remove(participant, "cognatepriming")) %>% 
	group_by(location, participant, lp, age_group, valid_participant) %>% 
	summarise(
		valid = mean(valid_trial),
		invalid_gaze = mean(!valid_gaze),
		invalid_vocab = mean(!valid_vocab),
		.groups = "drop"
	) %>% 
	relocate(participant) %>% 
	gt() %>% 
	tab_spanner(label = "Invalid trials", columns = starts_with("invalid_")) %>% 
	cols_label(
		participant = "Participant",
		location = "Location",
		lp = "Lang. Profile",
		age_group = "Age",
		valid_participant = "Valid participant",
		valid = "Valid trials (%)",
		invalid_gaze = "Gaze (%)",
		invalid_vocab = "Vocabulary (%)"
	) %>% 
	fmt_percent(c("valid", "invalid_gaze", "invalid_vocab")) %>% 
	as_raw_html()
```

@@

```{r trials_attrition_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(select(participants_stringent, participant, location)) %>% 
	group_by(location, lp, age_group, trial_type, valid_trial) %>% 
	count() %>% 
	ungroup() %>%
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Not valid")) %>% 
	pivot_wider(names_from = c(age_group, valid_trial), values_from = n, values_fill = 0) %>% 
	clean_names() %>% 
	gt(groupname_col = c("location", "lp")) %>% 
	tab_spanner(label = "21 months", columns = contains("21_")) %>% 
	tab_spanner(label = "25 months", columns = contains("25_")) %>% 
	tab_spanner(label = "30 months", columns = contains("30_")) %>% 
	cols_label(
		location = "Location",
		lp = "Group",
		trial_type = "Trial type",
		x21_months_not_valid = "Not valid",
		x21_months_valid = "Valid",
		x25_months_not_valid = "Not valid",
		x25_months_valid = "Valid",
		x30_months_not_valid = "Not valid",
		x30_months_valid = "Valid"
	) %>% 
	as_raw_html()

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	ggplot(aes(trial_type, frequency_prime_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

```{r attrition_frequency_prime_causes, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4, out.width="100%"}
# plot participants
attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_prime_childes)) %>% 
	drop_na(trial_type, frequency_prime_childes) %>% 
	mutate(frequency_prime_childes = round(frequency_prime_childes)) %>% 
	count(trial_type, age_group, valid_status, trial_type, frequency_prime_childes) %>% 
	ggplot(aes(as.factor(frequency_prime_childes), n, fill = valid_status, colour = valid_status)) +
	facet_grid(trial_type~age_group) +
	geom_col(position = position_fill(), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent) +
	coord_flip() +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, frequency_target_childes)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, frequency_target_childes) %>% 
	ggplot(aes(trial_type, frequency_target_childes, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 2, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Frequency (CHILDES)", colour = "Validity", fill = "Validity") +
	scale_y_continuous(breaks = 0:7, limits = c(0, 7)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_prime)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_prime) %>% 
	ggplot(aes(trial_type, familiarity_prime, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@

attrition %>% 
	left_join(distinct(stimuli, test_language, location, list, trial, trial_type, familiarity_target)) %>% 
	mutate(valid_status = ifelse(valid_status!="Valid", "Invalid", valid_status)) %>% 
	drop_na(trial_type, familiarity_target) %>% 
	ggplot(aes(trial_type, familiarity_target, fill = valid_status, colour = valid_status)) +
	facet_grid(lp~age_group) +
	geom_boxplot(fill = "white", width = 0.25,
				 position =  position_dodge(width = 0.5),
				 size = 1, outlier.colour = NA) +
	geom_label(data = sample_size, aes(y = 0.1, label = n), size = 3,
			   position = position_dodge(width = 0.7), colour = "white") +
	labs(x = "Trial type", y = "Trials", colour = "Validity", fill = "Validity") +
	guides(fill = guide_legend(ncol = 2), colour = guide_legend(ncol = 2))	+
	scale_y_continuous(labels = percent, limits = c(0, 1)) +
	theme(
		legend.position = "top",
		legend.title = element_blank(),
		panel.grid.major.y = element_line(colour = "grey", linetype = "dotted"),
		axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1, size = 10),
		axis.text.y = element_text(size = 8),
		axis.title = element_blank()
	)
```

@@
